---
title: "R Notebook: Myers Briggs Type Indicator Correlations"
output: html_notebook
---

## Description 

The Myers Briggs Type Indicator (MBTI) is a 4-letter code produced from a self-reported assessment designed to reflect an individual's personality traits. People of the same MBTI share common strengths & weaknesses, relationship characteristics, and habits. Theoretically, each person has their own unchanging Myers Briggs Type.

However, I found that my MBTI changed frequently based on how I interpreted the question and the information I used to come to an answer. This is an analysis of potential factors that could account for the changes in my MBTI over a course of 3 months. I retook the Myers Briggs Test on [16personalities.com](16personalities.com) once a week and additionally tracked daily change in the weather, sleep, and my mood on the following scales:

Weather: 4 = sunny; 3 = cloudy; 2 = windy; 1 = rainy

Mood: 5 = rad; 4 = great; 3 = meh; 2 = bad; 1 = awful

## Data Analysis

```{r}
#import libraries
library(readr)
library(dplyr)
library(plotly)

```


```{r}
# load and inspect datafile
data <- read_csv('Sem2Observations.csv')

data
```

```{r}
# clean dataframe
data <- data %>%
    filter(!is.na(sleep))

```

```{r}
# patterns per ESTP (correlations between weather, mood, MBTI)
estp <- data %>%
  filter(myers == 'ESTP') %>%
  group_by(weather, mood) 

rows = nrow(estp)

estp_freq <- estp %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percent = count * 100 / rows)
         
head(estp_freq)
```


```{r}
# patterns per ENFP (correlations between weather, mood, MBTI)
enfp <- data %>%
  filter(myers == 'ENFP') %>%
  group_by(weather, mood) 

rows = nrow(enfp)

enfp_freq <- enfp %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percent = count * 100 / rows)
         
head(enfp_freq)
```
The majority of the ENFP/ESTP (shared common factor of E - Extrovert) aligned with sunny weather and good mood (mood = 4, 5). The weather change can be explained by the period of time I moved from Princeton back home to California during the pandemic (March 16, 2020)

```{r}
# patterns per INFP (correlations between weather, mood, MBTI)
infp <- data %>%
  filter(myers == 'INFP') %>%
  group_by(weather, mood) 

rows = nrow(infp)

infp_freq <- infp %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percent = count * 100 / rows)
         
head(infp_freq)
```

ISFP had only one data point 
```{r}
# patterns per ISFP (correlations between weather, mood, MBTI)
isfp <- data %>%
  filter(myers == 'ISFP') %>%
  group_by(weather, mood) 

rows = nrow(infp)

isfp_count <- isfp %>%
  summarize(count = n()) 
         
head(isfp_count)
```

Below is an interactive 3D graph dispalying potential relationships between the variables and respective MBTI. Data appears to be very random.
```{r}
# 3D Graph
x <- data$weather
y <- data$sleep
z <- data$mood

myers <- c("ESTP", "ENFP", "INFP", "ISFP")
hex <- c("#DBC556", "#6CA673", "#805BB5", "#5687E9")

color_code <- data.frame(myers, hex)

colors <- data %>%
  left_join(color_code) %>%
  pull(hex)

fig <- plot_ly(data = data, x = ~weather, y = ~sleep, z = ~mood, 
          color = ~myers)
fig <- fig %>%
    add_markers() %>%
    layout(title = 'MBTI Relation with Mood, Sleep, Weather')
fig
```

Click/scroll over graph to interact